Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2025-10-28 manuscript_rmarkdown/manuscript.Rmd
Updated Latex file :)

---
title: "Location and Scale-Invariant Power Transformations for Transforming Data to
  Normality"
author: "Alex Zwanenburg, Steffen Löck"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: lualatex
    citation_package: natbib
    keep_tex: true
papersize: a4
bibliography: refs.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{amsthm}
- \usepackage{booktabs}
- \newtheorem*{definition}{Definition}
- \newtheorem*{corollary}[Corollary]
- \DeclareMathOperator*{\argmax}{argmax}
- \DeclareMathOperator*{\argmin}{argmin}
- \DeclareMathOperator{\sgn}{sgn}
---

@@

```{r empirical-central-normality-error_rate, warning=FALSE, message=FALSE, fig.cap=cap, fig.height=2.5}
cap <- paste0(
  "Observed type I error rates for central normality tests in the presence of data sampled from ",
  "central normal distributions with $\\kappa \\in \\left{0.6, 0.8, 1.0\\right}$. ",
  "Three empirical central normality (ECN) tests were performed, parameterised with same value for the central portion $\\kappa$. ",
  "Additionally, the Shapiro-Wilk test was assessed.",
  "ECN: empirical central normality"
)

>>>>

---
title: "Location and Scale-Invariant Power Transformations for Transforming Data to
  Normality"
author: "Alex Zwanenburg, Steffen Löck"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: lualatex
    citation_package: natbib
    keep_tex: true
papersize: a4
bibliography: refs.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{amsthm}
- \usepackage{booktabs}
- \newtheorem*{definition}{Definition}
- \newtheorem*{corollary}{Corollary}
- \DeclareMathOperator*{\argmax}{argmax}
- \DeclareMathOperator*{\argmin}{argmin}
- \DeclareMathOperator{\sgn}{sgn}
---

@@

```{r empirical-central-normality-error_rate, warning=FALSE, message=FALSE, fig.cap=cap, fig.height=2.5}
cap <- paste0(
  "Observed type I error rates for central normality tests in the presence of data sampled from ",
  "central normal distributions with $\\kappa \\in \\left\\{0.6, 0.8, 1.0\\right\\}$. ",
  "Three empirical central normality (ECN) tests were performed, parameterised with same value for the central portion $\\kappa$. ",
  "Additionally, the Shapiro-Wilk test was assessed. ",
  "ECN: empirical central normality"
)

### 2025-10-28 manuscript_rmarkdown/manuscript.tex
Updated Latex file :)

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
  a4paper,
]{article}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage[]{natbib}
\bibliographystyle{plainnat}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{booktabs}
\newtheorem*{definition}{Definition}
\newtheorem*{corollary}[Corollary]
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator{\sgn}{sgn}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Location and Scale-Invariant Power Transformations for Transforming Data to Normality},
  pdfauthor={Alex Zwanenburg, Steffen Löck},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\textbackslash begin\{figure\}

\{\centering \includegraphics{manuscript_files/figure-latex/empirical-central-normality-error_rate-1}

\}

\textbackslash caption\{Observed type I error rates for central
normality tests in the presence of data sampled from central normal
distributions with \$\kappa \in \left{0.6, 0.8, 1.0\right}\}. Three
empirical central normality (ECN) tests were performed, parameterised
with same value for the central portion \(\kappa\).Additional, the
Shapiro-Wilk test was assessed.ECN: empirical central
normality\}\label{fig:empirical-central-normality-error_rate}
\textbackslash end\{figure\}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
  a4paper,
]{article}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage[]{natbib}
\bibliographystyle{plainnat}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{booktabs}
\newtheorem*{definition}{Definition}
\newtheorem*{corollary}{Corollary}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator{\sgn}{sgn}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Location and Scale-Invariant Power Transformations for Transforming Data to Normality},
  pdfauthor={Alex Zwanenburg, Steffen Löck},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

{\centering \includegraphics{manuscript_files/figure-latex/empirical-central-normality-error_rate-1}

\caption{Observed type I error rates for central normality tests in the presence of data sampled from central normal distributions with $\kappa \in \left\{0.6, 0.8, 1.0\right\}$. Three empirical central normality (ECN) tests were performed, parameterised with same value for the central portion $\kappa$. Additionally, the Shapiro-Wilk test was assessed. ECN: empirical central normality}\label{fig:empirical-central-normality-error_rate}
\end{figure}
